### 2017-04-30 sec-conclusion.tex
Revised conclusions.

\section{Conclusion}
% summarize the main contributions of the paper; summarize the experimental
% results; argue again for our novelty; discuss future directions
We proposed a two-layer hidden Markov model for MOOC student behavior
modeling in an unsupervised learning framework on large collections of
actions extracted from MOOC log data. This model is different from existing
methods in that it treats behavior patterns as a sequence of \emph{latent
states}, rather than assigning these states in a rule-based manner. It
captures the variable behaviors of students over time, and allows
analysis at different levels of granularity.

We showed that such a model does in fact capture meaningful behavior
patterns and produces descriptions of these behavior patterns that are easy
to interpret. We argued that it is important to capture student behavior
patterns with more sophisticated models than simple discrete distributions
over actions in order to capture information present in bigrams of actions
(or above). By varying the number of latent
states inferred, we showed that the model is flexible and can capture
patterns of differing levels of specificity in this way.  Finally, we
investigated whether we can detect differences in student behavior patterns
as they correlate with course performance. Specifically, we demonstrated
that high-performing students produce substantially different HMM
transition diagrams that tend to show longer concentration span in quiz-taking
and more active  forum participation as compared with the average students.

>>>>

\section{Conclusion}
% summarize the main contributions of the paper; summarize the experimental
% results; argue again for our novelty; discuss future directions
As a tool to help instructors and eduation researchers better understand behavior of MOOC students, 
 we proposed a two-layer hidden Markov model to automatically extract 
student activity patterns in the form of behavior state-transition graphs from large amounts of 
MOOC log data. This model is different from existing
methods in that it treats behavior patterns as a sequence of \emph{latent
states}, rather than assigning these states in a rule-based manner. It
captures the variable behaviors of students over time, and allows
analysis at different levels of granularity.

We showed that such a model does in fact capture meaningful behavior
patterns and produces descriptions of these behavior patterns that are easy
to interpret. We argued that it is important to capture student behavior
patterns with more sophisticated models than simple discrete distributions
over actions in order to capture information present in bigrams of actions
(or above). By varying the number of latent
states inferred, we showed that the model is flexible and can capture
patterns of differing levels of specificity in this way.  Finally, we
investigated whether we can detect differences in student behavior patterns
as they correlate with course performance. Specifically, we demonstrated
that high-performing students produce substantially different HMM
transition diagrams that tend to show longer concentration span in quiz-taking
and more active  forum participation as compared with the average students.
These results show the great potential of the proposed model for serving as a tool
to help humans discovery knowledge about student behaviors.
